Supporting Information: Thermal sensitivity across forest vertical profiles: patterns, mechanisms, and ecological implications

### 2022-02-11 vertical-thermal-review.Rmd
incorporating some of R1's citations as necessary

---
title: ''
output: word_document
bibliography: Zotero_references.bib #This can be generated by exporting BibTex file from Zotero
csl: new-phytologist.csl 
nocite: |
  @mauTemperateTropicalForest2018; @cobleLightDrivesVertical2014; @sackHowStrongIntracanopy2006;@chinLeafAcclimationLight2017; @wykaResponsesLeafStructure2012; @athertonSpatialVariationLeaf2017; @kenzoHeightrelatedChangesLeaf2015; @kusiPlasticLeafMorphology2020; @dangProfilesPhotosyntheticallyActive1997;@gebauerEffectsProlongedDrought2015; @marencoLeafTraitPlasticity2017; @kafutiFoliarWoodTraits2020; @vanwittenbergheVariabilityStomatalConductance2012; @zhang_photosynthetic_2012; @weerasingheCanopyPositionAffects2014; @oldhamHydrostaticGradientNot2010; @ichieEcologicalDistributionLeaf2016a; @gregoriouEffectsReducedIrradiance2007; @levizouNondestructiveAssessmentLeaf2005; @liakouraTrichomeDensityIts1997; @fauset_differences_2018; @niinemetsAcclimationHighIrradiance1998; @millenLeafAngleAdaptive1979; @smithShootStructuralEffects1988; @hadleyInfluenceKrummholzMat1987; @panditharathnaChangeLeafStructure2008; @baltzerLeafOpticalResponses2005; @dietzVerticalPatternsDuration2007; @scartazzaInvestigatingEuropeanBeech2016a; @duursmaVerticalCanopyGradients2006; @harleyEffectsLightTemperature1996; @hernandezSimilarTemperatureDependence2020; @turnbullScalingFoliarRespiration2003; @chenLeafEconomicsSpectrum2020; @vandewegPhotosyntheticParametersDark2012; @cavaleri_foliar_2008; @konigerXanthophyllCyclePigmentsPhotosynthetic1995; @matsubaraSunshadePatternsLeaf2009; @harrisChangesLeafProperties2013; @hansenVariationPigmentComposition2002a; @poorterLeafOpticalProperties1995; @cobleHowVerticalPatterns2016; @niinemetsCanopyGradientsLeaf2004; @poorterLeafOpticalProperties2000; @taylorNewFieldInstrument2021; @harleyEnvironmentalControlsIsoprene1997; @niinemetsHowLightTemperature2015; @sharkeyFutureIsopreneEmission2014; @simpragaVerticalCanopyGradient2013; @zwienieckiHydraulicLimitationsImposed2004; @sackLeafVenationStructure2013; @ballMaintenanceLeafTemperature1988; @robertsStomatalBoundaryLayerConductances1990; @ambroseEffectsHeightTreetop2010; @zweifelMiddayStomatalClosure2002; @slotPhotosyntheticHeatTolerance2019; @urbanInductionPhotosynthesisImportance2007; @carterWithinCanopyExperimentalLeaf2018a; @martin_boundary_1999; @kosugiSeasonalFluctuationsTemperature2006; @niinemetsVariabilityLeafMorphology2015; @bachofenLightVPDGradients2020; @hamerlynckPhotosyntheticStomatalResponses1996a; @rijkersEffectTreeHeight2000a; @millerOnlySunlitLeaves2021; @legnerWithincanopyVariationPhotosynthetic2014; @kitaoCanopyNitrogenDistribution2018; @rey-sanchez_spatial_2016; @mullerEvidenceEfficientNonevaporative2021; @curtis_intracanopy_2019; @meirLeafRespirationTwo2001; @arakiVerticalSeasonalVariations2017; @bolstad_foliar_1999; @xuSeasonalVariationTemperature2006; @sackHydrologyLeavesCoordination2003; @niinemetsHighWithincanopyVariation2010; @brooksVerticalGradientsPhotosynthetic1997a
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

>>>>

---
title: ''
output: word_document
bibliography: Zotero_references.bib #This can be generated by exporting BibTex file from Zotero
csl: new-phytologist.csl 
nocite: |
  @mauTemperateTropicalForest2018; @cobleLightDrivesVertical2014; @sackHowStrongIntracanopy2006;@chinLeafAcclimationLight2017; @wykaResponsesLeafStructure2012; @athertonSpatialVariationLeaf2017; @kenzoHeightrelatedChangesLeaf2015; @kusiPlasticLeafMorphology2020; @dangProfilesPhotosyntheticallyActive1997;@gebauerEffectsProlongedDrought2015; @marencoLeafTraitPlasticity2017; @kafutiFoliarWoodTraits2020; @vanwittenbergheVariabilityStomatalConductance2012; @zhang_photosynthetic_2012; @weerasingheCanopyPositionAffects2014; @oldhamHydrostaticGradientNot2010; @ichieEcologicalDistributionLeaf2016a; @gregoriouEffectsReducedIrradiance2007; @levizouNondestructiveAssessmentLeaf2005; @liakouraTrichomeDensityIts1997; @fauset_differences_2018; @niinemetsAcclimationHighIrradiance1998; @millenLeafAngleAdaptive1979; @smithShootStructuralEffects1988; @hadleyInfluenceKrummholzMat1987; @panditharathnaChangeLeafStructure2008; @baltzerLeafOpticalResponses2005; @dietzVerticalPatternsDuration2007; @scartazzaInvestigatingEuropeanBeech2016a; @duursmaVerticalCanopyGradients2006; @harleyEffectsLightTemperature1996; @hernandezSimilarTemperatureDependence2020; @turnbullScalingFoliarRespiration2003; @chenLeafEconomicsSpectrum2020; @vandewegPhotosyntheticParametersDark2012; @cavaleri_foliar_2008; @konigerXanthophyllCyclePigmentsPhotosynthetic1995; @matsubaraSunshadePatternsLeaf2009; @harrisChangesLeafProperties2013; @hansenVariationPigmentComposition2002a; @poorterLeafOpticalProperties1995; @cobleHowVerticalPatterns2016; @niinemetsCanopyGradientsLeaf2004; @poorterLeafOpticalProperties2000; @taylorNewFieldInstrument2021; @harleyEnvironmentalControlsIsoprene1997; @niinemetsHowLightTemperature2015; @sharkeyFutureIsopreneEmission2014; @simpragaVerticalCanopyGradient2013; @zwienieckiHydraulicLimitationsImposed2004; @sackLeafVenationStructure2013; @ballMaintenanceLeafTemperature1988; @robertsStomatalBoundaryLayerConductances1990; @ambroseEffectsHeightTreetop2010; @zweifelMiddayStomatalClosure2002; @slotPhotosyntheticHeatTolerance2019; @urbanInductionPhotosynthesisImportance2007; @carterWithinCanopyExperimentalLeaf2018a; @martin_boundary_1999; @kosugiSeasonalFluctuationsTemperature2006; @niinemetsVariabilityLeafMorphology2015; @bachofenLightVPDGradients2020; @hamerlynckPhotosyntheticStomatalResponses1996a; @rijkersEffectTreeHeight2000a; @millerOnlySunlitLeaves2021; @legnerWithincanopyVariationPhotosynthetic2014; @kitaoCanopyNitrogenDistribution2018; @rey-sanchez_spatial_2016; @mullerEvidenceEfficientNonevaporative2021; @curtis_intracanopy_2019; @meirLeafRespirationTwo2001; @arakiVerticalSeasonalVariations2017; @bolstad_foliar_1999; @xuSeasonalVariationTemperature2006; @sackHydrologyLeavesCoordination2003; @niinemetsHighWithincanopyVariation2010; @brooksVerticalGradientsPhotosynthetic1997a; @carswellPhotosyntheticCapacityCentral2000
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
